\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-08 paper.tex
Summarized SPARK section

\subsection{Computed symbolic relations}

\subsubsection{Agent-independent locations}

Absolute spatial relations (\concept{isOn}, \concept{isIn}, \concept{isNextTo},
\concept{isAbove}...) are computed for every pair of objects, taking into
account relative sizes for relations like \concept{isNextTo}. Other
agent-independent properties like \concept{isMoving} are also computed.

\subsubsection{Agent-dependent placements}

The space surrounding each agent is divided into 16 regions (like
\emph{back-left}, \emph{front-near}, etc.). Based on this partition, symbolic
relations between each pair (agent, object) is computed and added to the
knowledge base.

\subsubsection{Affordances}

SPARK also computes affordances: \concept{sees}, \concept{looksAt},
\concept{pointsAt}, \concept{canReach}. Visibility (with two levels
corresponding to the field of view and the field of attention) and pointing are
computed by placing virtual cameras in the SPARK 3D model, while reachability
relies on inverse kinematics. Several filters (based on hysteresis, expected
object behaviour, etc.) allow to partially account for perception
noise~\cite{Warnier2012a}.

\subsection{Ego-centric and allo-centric frames}

SPARK enables \emph{perspective-taking}: spatial relations between entities can
be computed from different viewpoints, which let the robot build for each
agents it interacts with a different, \emph{perspective-aware} symbolic model
of the environment. These models are separately stored in the knowledge base.

@@

As a result, the robot stores models on the environment either in the
\emph{ego-centric} reference frame (from the robot perspective) or in
addressee-centred (\ie, \emph{allo-centric}) frames.

>>>>

\paragraph*{Computed symbolic relations} Over twenty physical relations are
continuously computed by SPARK: spatial relations, both agent-independent (like
\concept{isOn}, \concept{isNextTo} or \concept{isMoving}), and agent-dependent
(like \concept{isNear}, \concept{leftTo}), and also affordances:
\concept{sees}, \concept{looksAt}, \concept{pointsAt}, \concept{canReach}.
Visibility (with two levels corresponding to the field of view and the field of
attention) and pointing are computed by placing virtual cameras in the SPARK 3D
model, while reachability relies on inverse kinematics. Several filters (based
on hysteresis, expected object behaviour, etc.) allow to partially account for
perception noise~\cite{Warnier2012a}.

\paragraph*{Ego-centric and allo-centric frames} SPARK enables
\emph{perspective-taking}: spatial relations between entities can be computed
from different viewpoints, which let the robot build for each agents it
interacts with a different, \emph{perspective-aware} symbolic model of the
environment. These models are separately stored in the knowledge base.

@@

As a result, the robot stores models on the environment either in the
\emph{ego-centric} reference frame (from the robot perspective) or in the
\emph{allo-centric} frame (addressee-centred).
